---
title: "ScrapingData"
author: "David Chen"
date: "12/29/2019"
output: html_document
---

Note: This process will most likely break when the 2020 season starts. If you still want to use this code, change the following:  

+ Line 30 - change the year to your current year  
+ Line 34 - Change the link to the current season  
+ Line 56 - Change the end year to the previous season (2019 if you are in 2020)  

That should be the only necessary changes. Feel free to send me a message if more issues come up. 


```{r message = FALSE}
# Clean up R environment
rm(list = ls())

# Load in packages
library(tidyverse)
library(rvest)
```

Scrape the 2019 Data. 
```{r}
# Change this year if you are processing year 2020+
# This variable indicates year for this dataset
year <- 2019

# Change this link to the new season if desired
# Scrape the 2019 Data
NFL_link <- 'http://www.nfl.com/stats/categorystats?tabSeq=1&statisticPositionCategory=QUARTERBACK&qualified=true&season=2019&seasonType=REG'

NFL <- read_html(NFL_link)

# Scrape the data
Raw_table <-
  NFL_link %>%
  read_html() %>%
  html_nodes('table') %>%
  html_table(fill = T)


# Create the table that we will attach all the other years to
Full_Table <- 
  Raw_table[[1]] %>%
  distinct(Team, .keep_all = T) %>% # Keep only the top QB for every team
  mutate(Year = year)
```

Scrape the data from 1970-2018
```{r}
# Scrape years 1970-2018. Update the years if desired.
for (year in 1970:2018) {
  
  # Create the link to the stats for the year
  NFL_link <- paste0('http://www.nfl.com/stats/categorystats?archive=true&conference=null&statisticPositionCategory=QUARTERBACK&season=', year, '&seasonType=REG&experience=&tabSeq=1&qualified=true&Submit=Go')
  
  # Scrape the table
  Raw_table <-
    NFL_link %>%
    read_html() %>%
    html_nodes('table') %>%
    html_table(fill = T)

  # Extract the table and add a variable indicating the year
  Yearly_Table <- 
    Raw_table[[1]] %>%
    distinct(Team, .keep_all = T) %>% # Keep only the top QB for every team
    mutate(Year = year)

  # Attach all the data to the full table
  Full_Table <- rbind(Full_Table, Yearly_Table)
    
}
```

```{r}
# Sort and format the data before exporting
Full_Table <-
  Full_Table %>%
  arrange(desc(Year)) %>%
  mutate(Yds = as.numeric(gsub(",", "", Yds)))
```

Export the data. 
```{r}
# Save as an RDS (for loading the data easier in R)
saveRDS(Full_Table, file = "./Data/AllYearsQBData.rds")

# Save as a csv (for anybody else that wants to use the data)
write.csv(Full_Table, file = "./Data/AllYearsQBData.csv")
```


